### 2014-03-04 seminar/seminar_report/chapter5.tex
changes

    \begin{enumerate}
        \item Published a Journal Paper to the International Journal of Expert Systems With Applications; \emph{"To Compete or to Cooperate? This is the Question in Communities of Autonomous Services"}, 2014
        \item Published a Journal Paper to the IEEE Transactions on Services Computing; \emph{"Efficient Community Formation for Web Services"}, 2014
        \item Published a paper in 10th IEEE International Conference on Services Computing; \emph{"Efficient Coalition Formation for Web Services"}, 2013
        \item Published a Paper to the 10th International Conference on Service Oriented Computing; \emph{"Analyzing Coopetition Strategies of Services within Communities"}, 2012
    \end{enumerate}

>>>>

    \begin{enumerate}
        \item E. Khosrowshahi Asl, J. Bentahar, H. Otrok, R. Mizouni, \emph{``Efficient Community Formation for Web Services.''} Accepted at IEEE Transactions on Services Computing, Feb. 2014, IEEE. (Impact factor: 2.46)
        \item E. Khosrowshahi Asl, J. Bentahar, R. Mizouni, B. Khosravifar, H. Otrok, \emph{``To Compete or to Cooperate? This is the Question in Communities of Autonomous Services.''} In the Journal of Expert Systems and Applications, Feb. 2014, Elsevier. (Impact factor: 1.854, 5-year:  2.339)
        \item Published a conference paper in 10th IEEE International Conference on Services Computing; \emph{``Efficient Coalition Formation for Web Services''}, 2013
        \item Published a conference paper to the 10th International Conference on Service Oriented Computing; \emph{``Analyzing Coopetition Strategies of Services within Communities''}, 2012
    \end{enumerate}
